A Systematic Literature Review on Extensions to Role-Based Access Control

### 2013-05-01 paper/sections/analysis.tex
pdf upload and minior update

\begin{itemize}
	\item Addition: The extension model incorporates additional elements with regards to context/constraints and their relations with existing elements of the RBAC standard. Models in this category do not change the RBAC$_{m}$. We found 23 papers in this category.
	\item Modification: The extension model incorporates modification of existing features in the RBAC$_{m}$. For example, changes of attribute relations such as role hierarchy fall into this modification category. For models in this category, changes occur within the RBAC$_{m}$. We found one paper in this category.
	\item Combination: The extension model is a combination of RBAC$_{m}$ and another access control model, which uses model-specific attributes and their relations such as task, team, purpose, and organizational roles. For this combination, new associations between attributes of two models should be introduced. Models in this category require new associations between attributes of different access control models to work together. We found four papers in this category.
\end{itemize}

@@

RBAC$_{m}$ presents four entities: roles, sessions, users, and permissions, and their relations. While RBAC$_{m}$ is considered fundamental in any RBAC systems, RBAC$_{m}$ can be extended to be applicable for emerging applications such as healthcare and mobile devices. 
In such environments, the RBAC standard needs additional constraints and dynamic context to support dynamic environments such as spatial and location. For this category, more than 80\% of papers are classified into ``Addition'' category. Besides, one paper~\cite{alam06:constraint} describes modification of existing relationship among elements to support partial inheritance. The RBAC standard is shown to be combined with other access control models such as team-based access control and task-based access control~\cite{zhou2007team, oh2003task}.

>>>>

\begin{itemize}
	\item Addition: The extension model incorporates additional entities with regards to context/constraints and their relations with existing entities of the RBAC$_{m}$. Models in this category do not change the RBAC$_{m}$. We found 23 papers in this category.
	\item Modification: The extension model incorporates modification of existing features in the RBAC$_{m}$. For example, changes of attribute relations such as role hierarchy fall into this modification category. For models in this category, changes occur within the RBAC$_{m}$. We found one paper in this category.
	\item Combination: The extension model is a combination of RBAC$_{m}$ and another access control model, which uses model-specific attributes and their relations such as task, team, purpose, and organizational roles. For this combination, new associations between attributes of two models should be introduced. Models in this category require new associations between attributes of different access control models to work together. We found four papers in this category.
\end{itemize}

@@

RBAC$_{m}$ presents four entities: roles, sessions, users, and permissions, and their relations. While RBAC$_{m}$ is considered fundamental in any RBAC systems, RBAC$_{m}$ can be extended to be applicable for emerging applications such as healthcare and mobile devices. 
In such environments, the RBAC standard needs additional constraints and dynamic context to support dynamic environments such as spatial and location. For this category, more than 80\% of papers are classified into ``Addition'' category. Besides, one paper~\cite{alam06:constraint} describes modification of existing relationship among entities to support partial inheritance. The RBAC standard is shown to be combined with other access control models such as team-based access control and task-based access control~\cite{zhou2007team, oh2003task}.

### 2013-05-01 paper/sections/discussion.tex
pdf upload and minior update

A formal representation of access control models is a critical step of designing high-level abstraction where which elements are used and how elements are operated.
One of the objectives of a formal representation is to help ensure the correct behaviors through formal verification. Given the formal representation of access control models, software developers may prove of properties (e.g., safety, consistency and completeness) and check whether these properties are satisfied.

>>>>

A formal representation of access control models is a critical step of designing high-level abstraction where which entities are used and how these entities are operated.
One of the objectives of a formal representation is to help ensure the correct behaviors through formal verification. Given the formal representation of access control models, software developers may prove of properties (e.g., safety, consistency and completeness) and check whether these properties are satisfied.

### 2013-05-01 paper/sections/intro.tex
pdf upload and minior update

The use of RBAC has become popular since the National Institute for Standards and Technology (NIST) 
first proposed RBAC standard in the 1990s \cite{o20102010}.
The RBAC standard was first proposed when NIST 
requested that a unified standard be created by combining the Ferraiolo and Kuhn model \cite{ferraiolokuhn} with the framework 
proposed by Sandhu, et al \cite{sandhu1996role}.  
In 2004, this standard was adopted as ANSI/INCITS 359-2004 approved by American National Standards Institute (ANSI) and the InterNational Committee for Information Technology Standards (INCITS). 
The development of a standard was inspired by an economic impact study done during the 1990s and later confirmed in 2010 \footnote{\url{http://csrc.nist.gov/groups/SNS/rbac/documents/20101219_RBAC2_Final_Report.pdf}} that showed the cost savings of RBAC implementation and maintenance. 
Prior to the development of the RBAC standard, vendors proposed and implemented their own defined RBAC features without general agreement on a unified definition of RBAC or feature set. The RBAC standard includes RBAC reference models (RBAC$_{m}$ in short). RBAC$_{m}$ serve as a basis for defining scope of RBAC features and functional specifications of RBAC features.

>>>>

The use of RBAC has become popular since the National Institute for Standards and Technology (NIST) 
first proposed RBAC standard in the 1990s \cite{o20102010}.
The RBAC standard was first proposed when NIST 
requested that a unified standard be created by combining the Ferraiolo and Kuhn model \cite{ferraiolokuhn} with the framework 
proposed by Sandhu, et al \cite{sandhu1996role}.  
In 2004, this standard was adopted as ANSI/INCITS 359-2004 approved by American National Standards Institute (ANSI) and the InterNational Committee for Information Technology Standards (INCITS). 
The development of a standard was inspired by an economic impact study done during the 1990s and later confirmed in 2010\footnote{\url{http://csrc.nist.gov/groups/SNS/rbac/documents/20101219_RBAC2_Final_Report.pdf}} that showed the cost savings of RBAC implementation and maintenance. 
Prior to the development of the RBAC standard, vendors proposed and implemented their own defined RBAC features without general agreement on a unified definition of RBAC or feature set. The RBAC standard includes RBAC reference models (RBAC$_{m}$ in short). RBAC$_{m}$ serve as a basis for defining scope of RBAC features and functional specifications of RBAC features.
